An Airdrop That Preserves Recipient Privacy

### 2019-01-18 paper/defs.tex
in PAD definition, define parties S, R, V

\paragraph{Syntax} A private airdrop (PAD) system is a triple of efficient algorithms:
\begin{itemize}
\item $\text{sendTokens}(\PK) \to (c, s)$:
Generates a token $c$ to be posted on the blockchain,
and a secret~$s$ given to the recipient via a private channel.
For example, an encryption of $s$ under $\PK$ can be posted
to the blockchain.   The posted encrypted $s$ is not associated with 
the token $c$. 
\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}

\item $\text{sign}(\SK, (c, s), m) \to \sig$:
Signs a message $m$ indicating that the token $c$ is spent.

\item $\text{verify}(c, m, \sig) \to \{\text{yes},\text{no}\}:$
Verify that a signature $\sig$ on token $c$ is valid.
\end{itemize}

>>>>

In a private airdrop scheme PAD, a \emph{sender} \Sr creates a \emph{token}
    for a \emph{recipient} \Rt whose key pair is $(\PK, \SK)$, and posts
    this token in a transaction on a blockchain.
To claim the output of the transaction, \Rt generates a signature on a message
    indicating that the token is spent, and posts this message and signature
    to the blockchain.
Finally, any \emph{verifier} \Vr can check the signature on the message
    and the token.

\paragraph{Syntax} PAD is a triple of efficient algorithms:
%
\begin{itemize}
\item $\text{sendTokens}(\PK) \to (c, s)$:
%
\Sr generates token $c$ and secret $s$, posts $c$ publicly, and sends $s$
    to \Rt via some private channel.
%To send a \emph{token} $c$ to a \emph{recipient} \Rt whose key is $(\PK,
%    \SK)$, a \emph{sender} \Sr generates $c$ to be posted on a blockchain,
%    plus a \emph{secret}~$s$ given to \Rt via some private channel.
\unskip\footnote{For example, a encryption of $s$ under $\PK$ can be posted
    to a public messageboard. Note, however, that the posted ciphertext
    should not be publicly associated with the token $c$.}
%\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}

\item $\text{sign}(\SK, (c, s), m) \to \sig$:
\Rt generates signature $\sig$ over message $m$.

\item $\text{verify}(c, m, \sig) \to \{\text{yes},\text{no}\}:$
\Vr checks signature $\sig$ on message $m$ for token $c$.
\end{itemize}
